Tutorial_2a

### 2024-10-19 Tutorial_2a.Rmd
add effects tut2a

## Visualize posterior distributions of the effects of congruent and incongruent primes on cloglog-hazard relative to blank prime, for each time bin in trial 1000.

```{r post-distr}
post <-as_draws_df(model_M4) %>% # 8000 draws x 715 variables
   select(starts_with("b_")) %>%       # 8000 x 31
   expand_grid(period_9 = -3:6) %>%   
   mutate(period_9sq = period_9^2,
          period_9cu = period_9^3,
          trial100 = -900/1000)

# effects for trial 1000
plot_facet <- post %>% 
  mutate(Congruent = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3`,
         Incongruent = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` + period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3`) %>%

  pivot_longer(cols=Congruent:Incongruent, names_to = "condition" ) %>%
  select(condition, period_9, value) %>%
 # mutate(value_hr = exp(value)) %>%
  group_by(period_9) %>%

   ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-8,-6,-4,-2,0,2,4,6,8), limits = c(-8,8)) +
  labs(x = "time bin", y = "cloglog-hazard") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ condition)

@@

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_con_incon_trial1000.png", width = 12, height = 12, dpi = 300)
```

>>>>

## Visualize posterior distributions of the effects of congruent and incongruent primes on cloglog-hazard relative to blank prime, for each time bin in trials 500, 1000, and 1500.

```{r post-distr}
#get_variables(model_M4)[1:31]

post <-as_draws_df(model_M4) %>% # 8000 draws x 715 variables
   select(starts_with("b_")) %>%       # 8000 x 31
   expand_grid(period_9 = -3:6) %>%   
   mutate(period_9sq = period_9^2,
          period_9cu = period_9^3,
          trial500 = -500/1000,
          trial500sq = trial500^2,
          trial1500 = 500/1000,
          trial1500sq = trial1500^2)

# effects for trials 500, 1000, and 1500
effects <- post %>% 
  mutate(`congruent trial 1500` = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + 
            period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3` +
            trial1500 * `b_conditioncongruent:trial_c` + trial1500sq * `b_conditioncongruent:Itrial_cE2` +
            period_9 * trial1500 * `b_conditioncongruent:period_9:trial_c` +
            period_9sq * trial1500 * `b_conditioncongruent:Iperiod_9E2:trial_c` +
            period_9 * trial1500sq * `b_conditioncongruent:period_9:Itrial_cE2` +
            period_9sq * trial1500sq * `b_conditioncongruent:Iperiod_9E2:Itrial_cE2`,

         `incongruent trial 1500` = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` + 
            period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3` +
            trial1500 * `b_conditionincongruent:trial_c` + trial1500sq * `b_conditionincongruent:Itrial_cE2` +
            period_9 * trial1500 * `b_conditionincongruent:period_9:trial_c` +
            period_9sq * trial1500 * `b_conditionincongruent:Iperiod_9E2:trial_c` +
            period_9 * trial1500sq * `b_conditionincongruent:period_9:Itrial_cE2` +
            period_9sq * trial1500sq * `b_conditionincongruent:Iperiod_9E2:Itrial_cE2`,

         `congruent trial 500` = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + 
            period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3` +
            trial500 * `b_conditioncongruent:trial_c` + trial500sq * `b_conditioncongruent:Itrial_cE2` +
            period_9 * trial500 * `b_conditioncongruent:period_9:trial_c` +
            period_9sq * trial500 * `b_conditioncongruent:Iperiod_9E2:trial_c` +
            period_9 * trial500sq * `b_conditioncongruent:period_9:Itrial_cE2` +
            period_9sq * trial500sq * `b_conditioncongruent:Iperiod_9E2:Itrial_cE2`,

         `incongruent trial 500` = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` +
            period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3` +
            trial500 * `b_conditionincongruent:trial_c` + trial500sq * `b_conditionincongruent:Itrial_cE2` +
            period_9 * trial500 * `b_conditionincongruent:period_9:trial_c` +
            period_9sq * trial500 * `b_conditionincongruent:Iperiod_9E2:trial_c` +
            period_9 * trial500sq * `b_conditionincongruent:period_9:Itrial_cE2` +
            period_9sq * trial500sq * `b_conditionincongruent:Iperiod_9E2:Itrial_cE2`,

         `congruent trial 1000` = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + 
            period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3`,

         `incongruent trial 1000` = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` +
            period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3`) 
```

```{r plot-effects}
plot_facet <- effects %>%
  pivot_longer(cols=`congruent trial 1500`:`incongruent trial 1000`, names_to = "condition" ) %>%
  select(condition, period_9, value) %>%
  group_by(period_9) %>%

  ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-12,-10,-8,-6,-4,-2,0,2,4,6,8,10,12), limits = c(-12,12)) +
  labs(x = "time bin", y = "cloglog-hazard") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ factor(condition,levels=c("congruent trial 500","congruent trial 1000","congruent trial 1500","incongruent trial 500","incongruent trial 1000","incongruent trial 1500")))

@@

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_con_incon_3trials.png", width = 8, height = 8, dpi = 300)
```

# calculate point and interval estimates, and hazard ratios

```{r table-interval-estimates}
int_c_500 <- effects %>%
  select(`congruent trial 500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `hazard ratio` = exp(`congruent trial 500`),
         mean = `congruent trial 500`,
         condition = "c500") %>%
  select(bin_endpoint,condition, mean, .lower, .upper, .width, `hazard ratio`)

int_i_500 <- effects %>%
  select(`incongruent trial 500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `hazard ratio` = exp(`incongruent trial 500`),
         mean = `incongruent trial 500`,
         condition = "i500") %>%
  select(bin_endpoint, condition,mean, .lower, .upper, .width, `hazard ratio`)

int_c_1000 <- effects %>%
  select(`congruent trial 1000`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `hazard ratio` = exp(`congruent trial 1000`),
         mean = `congruent trial 1000`,
         condition = "c1000" ) %>%
  select(bin_endpoint,condition,mean, .lower, .upper, .width, `hazard ratio`)

int_i_1000 <- effects %>%
  select(`incongruent trial 1000`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `hazard ratio` = exp(`incongruent trial 1000`),
         mean = `incongruent trial 1000`,
         condition = "i1000") %>%
  select(bin_endpoint, condition,mean, .lower, .upper, .width,`hazard ratio`)

int_c_1500 <- effects %>%
  select(`congruent trial 1500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `hazard ratio` = exp(`congruent trial 1500`),
         mean = `congruent trial 1500`,
         condition = "c1500" ) %>%
  select(bin_endpoint, condition, mean, .lower, .upper, .width, `hazard ratio`)

int_i_1500 <- effects %>%
  select(`incongruent trial 1500`, period_9) %>%
  group_by(period_9) %>%
  mean_hdi() %>%
  mutate(bin_endpoint = (period_9 + 9)*40,
        `hazard ratio` = exp(`incongruent trial 1500`),
         mean = `incongruent trial 1500`,
         condition = "i1500") %>%
  select(bin_endpoint, condition,mean, .lower, .upper, .width,  `hazard ratio`)

test <- rbind(int_c_500, int_c_1000, int_c_1500,int_i_500,int_i_1000, int_i_1500)
test %>% print(n=60)
```

```{r save-table-interval-estimates, eval=F}
write_csv(test, file="Tutorial_2_Bayesian/tables/effects_intervals_table.csv")
```
